%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------
% -----------Multiple Positions Heading-----------
%    \resumeSubSubheading
%     {Software Engineer I}{Oct 2014 - Sep 2016}
%     \resumeItemListStart
%        \resumeItem{Apache Beam}
%          {Apache Beam is a unified model for defining both batch and streaming data-parallel processing pipelines}
%     \resumeItemListEnd
%    \resumeSubHeadingListEnd
%-------------------------------------------
\documentclass[letterpaper,10pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}
% \usepackage[margin=0.7in]{geometry}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.72in}
\addtolength{\evensidemargin}{-0.72in}
\addtolength{\textwidth}{1.44in}
\addtolength{\topmargin}{-0.72in}
\addtolength{\textheight}{1.44in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\mylink}[2]{%
    \textcolor{blue}{\underline{\href{#1}{#2}}}%
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*, label={}]}

\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\def \OpenUAEURL{https://www.sciencedirect.com/science/article/abs/pii/S1474034622001653}
\def \ISUdesign{https://conf.researchr.org/details/ase-2023/ase-2023-papers/105/Mutation-based-Fault-Localization-of-Deep-Neural-Networks}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    \textbf{\Huge \scshape Muhammad Arbab Arshad} \\ \vspace{1pt}
    \small 848-313-9857 $|$ \href{mailto:arbab@iastate.edu}{\underline{arbab@iastate.edu}} $|$ 
    \href{https://www.linkedin.com/in/arbab-arshad/ }{\underline{linkedin.com/in/arbab-arshad}} $|$
    \href{https://arbab-ml.github.io/}{\underline{arbab-ml.github.io}}
\end{center}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Iowa State University}{Iowa, USA}
      {Ph.D. (Computer Science)}{Jan. 2022 -- Dec 2025}
    \resumeSubheading
      {American University of Sharjah}{Sharjah, UAE}
      {M.S (Computer Engineering)}{Aug. 2019 -- Aug 2021}
    \resumeSubheading
      {Lahore University of Management Sciences}{Lahore, PK}
      {B.S (Computer Science)}{Aug. 2015 -- May 2019}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Machine Learning Engineer}{May 2020 -- Dec 2021}
      {OpenUAE }{Sharjah, UAE}
      \resumeItemListStart
        \resumeItem{Developed, optimized, and trained 12 ML models using \textbf{Python} on 50 million records to predict monthly electricity use in Dubai, achieving \underline{\emph{92.5\% accuracy}}.}
        \resumeItem{Proficiently applied \textbf{advanced linear algebra} and \textbf{probability} concepts during model optimization.}
        \resumeItem{Led a 6-person team in model analysis; achieved 10x faster training time leveraging advanced algorithmic optimization techniques~(\mylink{\OpenUAEURL}{URL}).}
        \resumeItem{Familiar with machine learning algorithms and utilized them in \textbf{data analysis} tasks to improve model accuracy.}
      \resumeItemListEnd
  
    \resumeSubheading
      {Research Assistant - ML}{May 2022 -- August 2022}
      {Laboratory for Software Design}{Iowa, USA}
      \resumeItemListStart
        \resumeItem{Executed 5 automated program repair tools for empirical studies on \textbf{SLURM-based GPU clusters} involving \textbf{machine learning algorithms}.}
        \resumeItem{Efficiently reduced execution time by \underline{\emph{16x}} by employing parallel execution of tools on 40 GPU clusters.}
        \resumeItem{Publication received a \underline{\emph{Distinguished Paper Award}} at the 38th IEEE/ACM International Conference on Automated Software Engineering~(\mylink{\ISUdesign}{URL}), demonstrating strong expertise in machine learning research.}
        \resumeItem{Used \textbf{Python} for prototyping and simulating algorithms, demonstrating a strong understanding of the programming language.}
      \resumeItemListEnd
  
    \resumeSubheading
      {Software Engineering Intern}{May 2022 -- August 2022}
      {Kingland}{Iowa, USA}
      \resumeItemListStart
        \resumeItem{Deployed auto-scaling in AWS Fargate and tested API; \textbf{embedded C/C++ programming} utilized for optimization.}
        \resumeItem{Constructed end-to-end pipeline for routine stress tests using \textbf{Python} and common packages, integrating JMeter for scripting and Blazemeter via Taurus for cloud execution.}
        \resumeItem{Customized GitLab CI/CD pipeline, emphasizing \textbf{SW/HW integration} and consistent testing.}      
        \resumeItem{Received formal \underline{\emph{recognition in two sprint retrospectives}} for establishing baseline for comprehensive load tests, showcasing commitment to quality.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
    
      \resumeProjectHeading
          {\textbf{Adapting Image Clustering for Audio Analysis of Bat Behaviors - Masters Thesis} $|$ \emph{Python, Keras, TensorFlow, PyTorch}}{}
          \resumeItemListStart
            \resumeItem{Utilized unsupervised ML techniques and \textbf{DSP} concepts to adapt image clustering algorithms to audio data for bat behavior analysis through echolocation calls.}
            \resumeItem{Employed algorithms such as IMSAT, IIC, SCAN, JULE, and DeepCluster, demonstrating proficiency in \textbf{machine learning} and \textbf{audio signal processing}, achieving an impressive \underline{\emph{88.28\% accuracy}} in bat classification.}
            \resumeItem{Showcased strong mathematical skills in \textbf{probability} and \textbf{advanced linear algebra} throughout the model development and optimization phases.}
          \resumeItemListEnd

      \resumeProjectHeading
          {\textbf{Utilizing GANs for Emotional Melody Generation} $|$ \emph{Python, Keras}}{}
          \resumeItemListStart
            \resumeItem{Leveraged Generative Adversarial Networks (GANs) to develop a text-to-audio generation system transforming poetry into melody, aligning with \textbf{audio signal processing} expertise.}
            \resumeItem{Achieved melodies with \underline{\emph{68\% perceived similarity}} to real melodies, emphasizing the practical application of machine learning algorithms in real-world scenarios.}
          \resumeItemListEnd

      \resumeProjectHeading
          {\textbf{Amazon Elastic Inference for assistance in Intrusion Detection} $|$ \emph{Java, AWS EC2, Keras}}{}
          \resumeItemListStart
            \resumeItem{Leveraged Amazon Elastic Inference (EI) for remote detection of SSH and FTP brute-force attacks in traffic data, showcasing proficiency in real-time \textbf{data analysis}.}
            \resumeItem{Achieved a high \underline{\emph{F1 score of 99\%}} and augmented speed by \underline{\emph{8x}} using EI for model deployment, emphasizing the project's success and scalability.}
          \resumeItemListEnd

      \resumeProjectHeading
          {\textbf{MeditateGPT} $|$ \emph{MERN Stack, GPT-3 API, Amazon Polly, AWS S3}}{}
          \resumeItemListStart
            \resumeItem{Developed MeditateGPT, a user-centric application, enabling personalized guided meditation sessions through GPT-3.}
            \resumeItem{Employed SSML and Amazon Polly's TTS API to craft natural-sounding audio, reflecting proficiency in synthesizing and processing audio signals.}
          \resumeItemListEnd

    \resumeSubHeadingListEnd



%
%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Programming \& Prototyping}{: Python (with common packages such as Scikit-learn, TensorFlow, PyTorch, OpenCV), MATLAB, Embedded C/C++, Java} \\
     \textbf{Deep Learning}{: Keras, CUDA, GPT-3 API, Unsupervised Deep Learning} \\
     \textbf{Signal Processing \& Robotics Algorithms}{: Digital Signal Processing (DSP), Kalman Filter, Particle Filter, SLAM, Audio Signal Processing} \\
     \textbf{Mathematics}{: Probability, Advanced Linear Algebra, Statistics, Calculus} \\
     \textbf{General}{: Git, SQL} \\
     \textbf{Amazon Web Services}{: Compute (EC2, Lambda), Storage (S3), Networking (VPC, ELB), Cloud (IAM, KMS, Amazon Polly), Data Analysis and Visualization}
     \textbf{Communication Protocols}{: Ethernet, CAN (Experience preferred)}
    }}
 \end{itemize}

%-------------------------------------------
\end{document}
