%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------
% -----------Multiple Positions Heading-----------
%    \resumeSubSubheading
%     {Software Engineer I}{Oct 2014 - Sep 2016}
%     \resumeItemListStart
%        \resumeItem{Apache Beam}
%          {Apache Beam is a unified model for defining both batch and streaming data-parallel processing pipelines}
%     \resumeItemListEnd
%    \resumeSubHeadingListEnd
%-------------------------------------------
\documentclass[letterpaper,10pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}
% \usepackage[margin=0.7in]{geometry}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.72in}
\addtolength{\evensidemargin}{-0.72in}
\addtolength{\textwidth}{1.44in}
\addtolength{\topmargin}{-0.72in}
\addtolength{\textheight}{1.44in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\mylink}[2]{%
    \textcolor{blue}{\underline{\href{#1}{#2}}}%
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*, label={}]}

\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\def \OpenUAEURL{https://www.sciencedirect.com/science/article/abs/pii/S1474034622001653}
\def \ISUdesign{https://conf.researchr.org/details/ase-2023/ase-2023-papers/105/Mutation-based-Fault-Localization-of-Deep-Neural-Networks}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    \textbf{\Huge \scshape Muhammad Arbab Arshad} \\ \vspace{1pt}
    \small 848-313-9857 $|$ \href{mailto:arbab@iastate.edu}{\underline{arbab@iastate.edu}} $|$ 
    \href{https://www.linkedin.com/in/arbab-arshad/ }{\underline{linkedin.com/in/arbab-arshad}} $|$
    \href{https://arbab-ml.github.io/}{\underline{arbab-ml.github.io}}
\end{center}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Iowa State University}{Iowa, USA}
      {Ph.D. (Computer Science)}{Jan. 2022 -- Dec 2025}
    \resumeSubheading
      {American University of Sharjah}{Sharjah, UAE}
      {M.S (Computer Engineering)}{Aug. 2019 -- Aug 2021}
    \resumeSubheading
      {Lahore University of Management Sciences}{Lahore, PK}
      {B.S (Computer Science)}{Aug. 2015 -- May 2019}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------
\section{Experience}
\resumeSubHeadingListStart
vbnet
Copy code
\resumeSubheading
  {Research Assistant - Machine Learning}{May 2022 -- August 2022}
  {Laboratory for Software Design}{Iowa, USA}
  \resumeItemListStart
    \resumeItem{Designed and executed \underline{\emph{Machine Learning algorithms}} as part of an empirical study on SLURM-based GPU clusters, using tools like Python and Java.}
    \resumeItem{Innovatively reduced execution time by 16x by enabling parallel tool processing on 40 GPU clusters, showcasing a strong ability to think outside the box.}
    \resumeItem{Collaborated with a diverse team and contributed to the publication that received a \underline{\emph{Distinguished Paper Award}} at the 38th IEEE/ACM International Conference on Automated Software Engineering~(\mylink{\ISUdesign}{URL}), illustrating profound research experience in Machine Learning.}
  \resumeItemListEnd

\resumeSubheading
  {Machine Learning Engineer}{May 2020 -- Dec 2021}
  {OpenUAE }{Sharjah, UAE}
  \resumeItemListStart
    \resumeItem{Skillfully developed and optimized 12 ML models using Python, handling 50 million records to predict monthly electricity use, and achieved a remarkable 92.5\% accuracy.}
    \resumeItem{Demonstrated leadership skills by heading a 6-person team in model analysis and employed advanced algorithmic optimization techniques to achieve 10x faster training time~(\mylink{\OpenUAEURL}{URL}).}
    \resumeItem{Regularly collaborated with interdisciplinary teams, showcasing excellent interpersonal skills and a drive to produce outstanding results.}
  \resumeItemListEnd
  
\resumeSubheading
  {Software Engineering Intern}{05/2022 -- 08/2022}
  {Kingland}{Iowa, USA}
  \resumeItemListStart
    \resumeItem{Executed auto-scaling in AWS Fargate using Java, stress-tested API to validate container duplication, and ensured optimal resource usage.}
    \resumeItem{Constructed a comprehensive pipeline for routine stress tests using JMeter and Blazemeter via Taurus, emphasizing proficiency in large scale data processing.}
    \resumeItem{Customized GitLab CI/CD pipeline ensuring seamless test executions with no disruptions, demonstrating keen analytical and problem-solving skills.}
    \resumeItem{Achieved formal \underline{\emph{recognition in two sprint retrospectives}} for setting the standard for comprehensive load tests and consistently showcasing a results-driven approach.}
  \resumeItemListEnd
  
\resumeSubHeadingListEnd


%-----------PROJECTS-----------
\section{Projects}
\resumeSubHeadingListStart
vbnet
Copy code
  \resumeProjectHeading
      {\textbf{Adapting Image Clustering for Audio Analysis of Bat Behaviors - Masters Thesis} $|$ \emph{Python, TensorFlow, Keras, PyTorch}}{}
      \resumeItemListStart
        \resumeItem{Pioneered the adaptation of unsupervised ML image clustering algorithms for audio data analysis using tools like Python and TensorFlow.}
        \resumeItem{Implemented cutting-edge algorithms such as IMSAT, IIC, SCAN, JULE, and DeepCluster, demonstrating proficiency in deep learning and achieving an accuracy of 88.28\% in classifying bats.}
      \resumeItemListEnd

  \resumeProjectHeading
      {\textbf{Amazon Elastic Inference for Intrusion Detection} $|$ \emph{Java, AWS EC2, Keras}}{}
      \resumeItemListStart
        \resumeItem{Developed a novel approach using Amazon Elastic Inference (EI) for remote detection of SSH and FTP brute-force attacks, demonstrating hands-on experience with large scale data processing.}
        \resumeItem{Achieved an impressive F1 score of 99\% and enhanced inference speed by 8x with the model on EI compared to local methods, highlighting analytical and problem-solving abilities.}
      \resumeItemListEnd
  
  \resumeProjectHeading
      {\textbf{Utilizing GANs for Emotional Melody Generation} $|$ \emph{Python, Keras}}{}
      \resumeItemListStart
        \resumeItem{Innovatively developed a poetry-to-melody generation system using Generative Adversarial Networks (GANs), showcasing expertise in AI and Deep Learning.}
        \resumeItem{Generated melodies that bore a 68\% perceived similarity to authentic melodies, emphasizing my ability to think outside the box.}
      \resumeItemListEnd

  \resumeProjectHeading
      {\textbf{MeditateGPT} $|$ \emph{MERN Stack, GPT-3 API, Amazon Polly, AWS S3}}{}
      \resumeItemListStart
        \resumeItem{Engineered MeditateGPT, a unique application for tailored guided meditations utilizing the GPT-3 API, underlining a drive for innovation in the field of AI.}
        \resumeItem{Integrated SSML and Amazon Polly's TTS API for synthesis of authentic-sounding audio, reflecting strong collaborative and technical skills.}
      \resumeItemListEnd

\resumeSubHeadingListEnd



%
%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
\begin{itemize}[leftmargin=0.15in, label={}]
\small{\item{
\textbf{Languages}{: C++, Java, Python, R, MATLAB} \
\textbf{Deep Learning}{: TensorFlow, PyTorch, Keras, CUDA, Scikit-learn, OpenCV, GPT-3 API, Unsupervised Techniques} \
\textbf{Data Processing and Analytics}{: Hadoop, MapReduce, SQL} \
\textbf{Amazon Web Services}{: EC2, Lambda, S3, VPC, ELB, IAM, KMS, Amazon Polly} \
\textbf{General Tools}{: Git} \
}}
\end{itemize}

%-------------------------------------------
\end{document}
