%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------
% -----------Multiple Positions Heading-----------
%    \resumeSubSubheading
%     {Software Engineer I}{Oct 2014 - Sep 2016}
%     \resumeItemListStart
%        \resumeItem{Apache Beam}
%          {Apache Beam is a unified model for defining both batch and streaming data-parallel processing pipelines}
%     \resumeItemListEnd
%    \resumeSubHeadingListEnd
%-------------------------------------------
\documentclass[letterpaper,10pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}
% \usepackage[margin=0.7in]{geometry}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.72in}
\addtolength{\evensidemargin}{-0.72in}
\addtolength{\textwidth}{1.44in}
\addtolength{\topmargin}{-0.72in}
\addtolength{\textheight}{1.44in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\mylink}[2]{%
    \textcolor{blue}{\underline{\href{#1}{#2}}}%
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*, label={}]}

\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\def \OpenUAEURL{https://www.sciencedirect.com/science/article/abs/pii/S1474034622001653}
\def \ISUdesign{https://conf.researchr.org/details/ase-2023/ase-2023-papers/105/Mutation-based-Fault-Localization-of-Deep-Neural-Networks}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    \textbf{\Huge \scshape Muhammad Arbab Arshad} \\ \vspace{1pt}
    \small 848-313-9857 $|$ \href{mailto:arbab@iastate.edu}{\underline{arbab@iastate.edu}} $|$ 
    \href{https://www.linkedin.com/in/arbab-arshad/ }{\underline{linkedin.com/in/arbab-arshad}} $|$
    \href{https://arbab-ml.github.io/}{\underline{arbab-ml.github.io}}
\end{center}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Iowa State University}{Iowa, USA}
      {Ph.D. (Computer Science)}{Jan. 2022 -- Dec 2025}
    \resumeSubheading
      {American University of Sharjah}{Sharjah, UAE}
      {M.S (Computer Engineering)}{Aug. 2019 -- Aug 2021}
    \resumeSubheading
      {Lahore University of Management Sciences}{Lahore, PK}
      {B.S (Computer Science)}{Aug. 2015 -- May 2019}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Research Assistant - ML}{May 2022 -- August 2022}
      {Laboratory for Software Design}{Iowa, USA}
      \resumeItemListStart
        \resumeItem{Architected and executed 5 automated program repair tools using \textbf{deep learning} and \textbf{computer vision} methodologies on SLURM-based GPU clusters.}
        \resumeItem{Achieved \underline{\emph{16x faster execution time}} via parallel processing on 40 GPU clusters, demonstrating proficiency in distributed systems.}
        \resumeItem{\textbf{Publication recognized with a \underline{\emph{Distinguished Paper Award}}} at the 38th IEEE/ACM International Conference on Automated Software Engineering, highlighting advanced research capabilities~(\mylink{\ISUdesign}{URL}).}
      \resumeItemListEnd

    \resumeSubheading
      {Machine Learning Engineer}{May 2020 -- Dec 2021}
      {OpenUAE }{Sharjah, UAE}
      \resumeItemListStart
        \resumeItem{Designed and refined 12 ML algorithms in \textbf{Python} for predicting monthly electricity usage, attaining \underline{\emph{92.5\% prediction accuracy}} with 50 million datasets.}
        \resumeItem{Headed a team of 6 in in-depth model analysis and optimization; realized \underline{\emph{10x faster training times}} via advanced algorithm techniques, showcasing deep understanding of dynamics and controls~(\mylink{\OpenUAEURL}{URL}).}
      \resumeItemListEnd
    
    \resumeSubheading
      {Software Engineering Intern}{05/2022 -- 08/2022}
      {Kingland}{Iowa, USA}
      \resumeItemListStart
        \resumeItem{Designed an auto-scaling feature in AWS Fargate using \textbf{C++} and stress-tested API to validate container replication, ensuring optimized resource consumption.}
        \resumeItem{Established a pipeline for routine stress tests using JMeter and Blazemeter (via Taurus), embodying a commitment to writing clean, well-architected code.}
        \resumeItem{Custom-tailored GitLab CI/CD pipeline for seamless test executions, ensuring consistent resource integrity in a collaborative, fast-paced environment.}
        \resumeItem{Earned formal \underline{\emph{acknowledgment in two sprint retrospectives}} for laying the groundwork for comprehensive load assessments.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
    
      \resumeProjectHeading
          {\textbf{Adapting Image Clustering for Audio Analysis of Bat Behaviors - Masters Thesis} $|$ \emph{Python, Keras, TensorFlow, PyTorch}}{}
          \resumeItemListStart
            \resumeItem{Pioneered the adaptation of unsupervised \textbf{ML image clustering algorithms} to audio data for understanding bat behaviors via echolocation patterns.}
            \resumeItem{Employed deep learning techniques like IMSAT, IIC, SCAN, JULE, and DeepCluster, resulting in \underline{\emph{88.28\% classification accuracy}} for differentiating bat species.}
          \resumeItemListEnd

      \resumeProjectHeading
          {\textbf{Utilizing GANs for Emotional Melody Generation} $|$ \emph{Python, Keras}}{}
          \resumeItemListStart
            \resumeItem{Innovated a text-to-audio generation framework transforming poetry into melody using \textbf{Generative Adversarial Networks (GANs)}; a venture into \textbf{deep learning} and \textbf{computer vision}.}
            \resumeItem{Generated compositions exhibiting \underline{\emph{68\% perceived similarity}} to authentic melodies, indicating the system's efficiency in creating lifelike sequences.}
          \resumeItemListEnd

      \resumeProjectHeading
          {\textbf{Amazon Elastic Inference for Intrusion Detection} $|$ \emph{Java, AWS EC2, Keras}}{}
          \resumeItemListStart
            \resumeItem{Harnessed Amazon Elastic Inference to remotely identify SSH and FTP brute-force assaults in traffic datasets, emphasizing real-time \textbf{embedded software} solutions.}
            \resumeItem{Marked a remarkable \underline{\emph{99\% F1 score}}, and achieved an \underline{\emph{8x speed increment}} in model evaluation on EI as opposed to local evaluations.}
          \resumeItemListEnd

      \resumeProjectHeading
          {\textbf{MeditateGPT} $|$ \emph{MERN Stack, GPT-3 API, Amazon Polly, AWS S3}}{}
          \resumeItemListStart
            \resumeItem{Conceived and launched MeditateGPT, a tailored guided meditation platform leveraging GPT-3, offering users a tailored meditation experience.}
            \resumeItem{Integrated SSML with Amazon Polly's TTS API, producing naturalistic audio sessions, showcasing an intersection of AI and user experience.}
          \resumeItemListEnd

    \resumeSubHeadingListEnd



%
%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Programming Languages}{: High proficiency in C++, Python, and Java} \\
     \textbf{Deep Learning and Computer Vision}{: TensorFlow, PyTorch, Keras, OpenCV, Unsupervised Deep Learning, CUDA, Scikit-learn, GPT-3 API} \\
     \textbf{General Software Development}{: Git, SQL, MATLAB, Software Architecture and Design Patterns} \\
     \textbf{Distributed Systems and AWS}{: EC2, Lambda, S3, VPC, ELB, IAM, KMS, Amazon Polly} \\
     \textbf{Other}{: R, Dynamics and Controls, Motion Planning, 3D Graphics}
    }}
 \end{itemize}

%-------------------------------------------
\end{document}
